---
title: "Table 2 - Total Household Wealth"
output: word_document
date: '2022-03-15'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE, echo=FALSE}
library(tidyverse)
library(parallel)
library(cmdstanr)
library(brms)
library(rstan)
library(posterior)
#library(magrittr)
library(knitr)
library(broom)
library(broom.mixed)
library(tidybayes)
library(bayesplot)
library(bayestestR)
library(kableExtra)
library(xtable)
library(sjPlot)
#library(texreg)
#library(kableExtra)
library(tidymodels)
library(estimatr)
library(Hmisc)
library(vip)
library(car)
library(sandwich)
```


Load the **total household wealth** model variables

```{r, include=FALSE, echo=FALSE}
# run linear model again using the bayesian "brms" package
hh_wealth_data <- read_csv("gik_hh_main.csv") %>%
  select(hhid, round, vid, block, eligible, samp_wgt, cost_deviation,
         treat_any, treat_GK, # treatment dummies
         wealth_asinh, # Outcome variable
         wealth_asinh_R1, # Baseline value of wealth_asinh, present in both rounds
         Lhh_wealth_asinh, Lvill_eligible_ratio, Lowndwelling) # controls
# view(per_cap_consumption_data)
```


**total household wealth**: This is the basic benchmarking model utilizing `brm()` default, uninformed priors

household wealth model with Lhh_wealth_asinh. This model does not converge due to colinearity issues caused by the Lhh_wealth_asinh variable 
```{r}
hh_wealth_bayesmodel_old <-
  brm(formula = wealth_asinh | weights(samp_wgt) ~
        cost_deviation + treat_any + treat_GK +
        wealth_asinh_R1 + Lhh_wealth_asinh + Lvill_eligible_ratio + Lowndwelling +
        (1 | block) + (1 | vid),
     data = hh_wealth_data,
     family = gaussian("identity"),
     seed = 1272022,
     warmup = 1000,
     iter = 2000,
     thin = 1,
     control = list(adapt_delta = .95, max_treedepth = 10),
     #backend = "cmdstanr",
     cores = 4, #overrides default 1 core
     #threads = 3,need to get cmdstanr package working here
     save_pars = save_pars(all = TRUE), # potentially allows for more post-processing functionality
     file = "uninformed_prior_outcomes\\hh_wealth_bayes_old")
```

```{r}
hh_wealth_bayesmodel <-
  brm(formula = wealth_asinh | weights(samp_wgt) ~
        cost_deviation + treat_any + treat_GK +
        wealth_asinh_R1 + Lvill_eligible_ratio + Lowndwelling +
        (1 | block) + (1 | vid),
     data = hh_wealth_data,
     family = gaussian("identity"),
     seed = 1272022,
     warmup = 1000,
     iter = 2000,
     thin = 1,
     control = list(adapt_delta = .95, max_treedepth = 10),
     #backend = "cmdstanr",
     cores = 4, #overrides default 1 core
     #threads = 3,need to get cmdstanr package working here
     save_pars = save_pars(all = TRUE), # potentially allows for more post-processing functionality
     file = "uninformed_prior_outcomes\\hh_wealth_bayes")
```

Model Summaries
```{r}
summary(hh_wealth_bayesmodel_old)
summary(hh_wealth_bayesmodel)
```

Prior summery - how informative are priors
```{r}
prior_summary(hh_wealth_bayesmodel_old)
check_prior(hh_wealth_bayesmodel_old)

prior_summary(hh_wealth_bayesmodel)
check_prior(hh_wealth_bayesmodel)
```

Diagnostics
```{r}
# trace diagnostic plot
mcmc_trace(hh_wealth_bayesmodel_old, n_warmup = 0,
           pars = c("b_Intercept", "b_cost_deviation", "b_treat_any", 
                    "b_treat_GK", "b_wealth_asinh_R1", "b_Lhh_wealth_asinh",
                    "b_Lvill_eligible_ratio", "b_Lowndwelling",
                    "sd_block__Intercept", "sd_vid__Intercept", "sigma"))
ggsave("table_2_diagnostics\\hh_wealth_trace_old.png", plot = last_plot(), width = 12, height = 5)

mcmc_trace(hh_wealth_bayesmodel, n_warmup = 0,
           pars = c("b_Intercept", "b_cost_deviation", "b_treat_any", 
                    "b_treat_GK", "b_wealth_asinh_R1",
                    "b_Lvill_eligible_ratio", "b_Lowndwelling",
                    "sd_block__Intercept", "sd_vid__Intercept", "sigma"))
ggsave("table_2_diagnostics\\hh_wealth_trace.png", plot = last_plot(), width = 12, height = 5)

#density diagnostic plot
mcmc_dens(hh_wealth_bayesmodel_old,
           pars = c("b_Intercept", "b_cost_deviation", "b_treat_any", 
                    "b_treat_GK", "b_wealth_asinh_R1", "b_Lhh_wealth_asinh",
                    "b_Lvill_eligible_ratio", "b_Lowndwelling",
                    "sd_block__Intercept", "sd_vid__Intercept", "sigma"))
ggsave("table_2_diagnostics\\hh_wealth_dens_old.png", plot = last_plot(), width = 12, height = 5)

mcmc_dens(hh_wealth_bayesmodel,
           pars = c("b_Intercept", "b_cost_deviation", "b_treat_any", 
                    "b_treat_GK", "b_wealth_asinh_R1",
                    "b_Lvill_eligible_ratio", "b_Lowndwelling",
                    "sd_block__Intercept", "sd_vid__Intercept", "sigma"))
ggsave("table_2_diagnostics\\hh_wealth_dens.png", plot = last_plot(), width = 12, height = 5)

mcmc_dens_overlay(hh_wealth_bayesmodel_old,
           pars = c("b_Intercept", "b_cost_deviation", "b_treat_any", 
                    "b_treat_GK", "b_wealth_asinh_R1", "b_Lhh_wealth_asinh",
                    "b_Lvill_eligible_ratio", "b_Lowndwelling",
                    "sd_block__Intercept", "sd_vid__Intercept", "sigma"))
ggsave("table_2_diagnostics\\hh_wealth_dens_overlay_old.png", plot = last_plot(), width = 12, height = 5)

mcmc_dens_overlay(hh_wealth_bayesmodel,
           pars = c("b_Intercept", "b_cost_deviation", "b_treat_any", 
                    "b_treat_GK", "b_wealth_asinh_R1",
                    "b_Lvill_eligible_ratio", "b_Lowndwelling",
                    "sd_block__Intercept", "sd_vid__Intercept", "sigma"))
ggsave("table_2_diagnostics\\hh_wealth_dens_overlay.png", plot = last_plot(), width = 12, height = 5)

#acf (auto-correlation) diagnostic plot
mcmc_acf(hh_wealth_bayesmodel_old,
           pars = c("b_Intercept", "b_cost_deviation", "b_treat_any", 
                    "b_treat_GK", "b_wealth_asinh_R1", "b_Lhh_wealth_asinh",
                    "b_Lvill_eligible_ratio", "b_Lowndwelling",
                    "sd_block__Intercept", "sd_vid__Intercept", "sigma"))
ggsave("table_2_diagnostics\\hh_wealth_acf_old.png", plot = last_plot(), width = 12, height = 5)

mcmc_acf(hh_wealth_bayesmodel,
           pars = c("b_Intercept", "b_cost_deviation", "b_treat_any", 
                    "b_treat_GK", "b_wealth_asinh_R1",
                    "b_Lvill_eligible_ratio", "b_Lowndwelling",
                    "sd_block__Intercept", "sd_vid__Intercept", "sigma"))
ggsave("table_2_diagnostics\\hh_wealth_acf.png", plot = last_plot(), width = 12, height = 5)
```

posterior predictive checks
```{r}
pp_check(hh_wealth_bayesmodel, nsamples = 100)
pp_check(hh_wealth_bayesmodel, nsamples = 10, type = 'error_scatter_avg', alpha = .1)
```